\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
%\usepackage[hidelinks]{hyperref}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{cite}
\usepackage[version=4]{mhchem} % for isotope symbols
\usepackage{a4wide}
\usepackage[lmargin=1cm,rmargin=1cm,tmargin=1cm,bmargin=2cm,headheight=0in]{geometry}
\usepackage{amssymb}


\hypersetup{colorlinks, linkcolor={blue!50!black}, citecolor={blue!50!black},
	urlcolor={blue!50!black}}

\begin{document}
\title{Journal Entry - Week Five - Entry Four}
\author{Caspian Nicholls, u1027945}
\date{\today}

\maketitle

\noindent
I give permission for portions of this work to be used as examples in future science communication course notes.
% \textit{[Delete if you don't want to do this]}\\

\medskip
\noindent
\textbf{Article title:} Search for octupole correlations in neutron-rich $\ce{^{148}Ce}$ nucleus \\
\textbf{Authors:} Y. J. Chen, S. J. Zhu, J. H. Hamilton, A. V. Ramayya, J. K. Hwang, M. Sakhaee, Y. X. Luo, J. O. Rasmussen, K. Li, I. Y. Lee, X. L. Che, H. B. Ding, and M. L. Li \\
\textbf{Reference:} Phys. Rev. C 73, 054316, May 2006. \\
\textbf{Link:}  \href{10.1103/PhysRevC.73.054316}{Article abstract}. \\
\textbf{Word count:} 750.
%\textit{Give the word count of everything below this point, e.g. copy paste into the \href{https://app.uio.no/ifi/texcount/online.php}{TeXcount} online tool. 750 word limit.}

\section*{Context}
%Briefly summarise the background of the area of physics relevant to the problem they are solving. Why it is an important or relevant area and problem?
Interactions between nucleons within nuclei can affect nuclear shapes. One such interaction is that of octupole correlations, the observation of which can provide evidence that a nucleus possesses a non-spherical (often pear-shaped) charge distribution. These correlations arise when nucleons in nuclear orbitals that have opposite parity (positive and negative) and a precise relationship between their quantum numbers interact strongly. Specifically, the interacting orbitals will satisfy $\Delta n = 1$ and $\Delta l = \Delta j = 3$, where $n$, $l$ and $j$ denote the principal, orbital angular momentum and total angular momentum quantum numbers.

\medskip
Theoretical calculations that utilise accepted models of nuclear structure predict that several nuclei with proton number $Z \sim 56$ and neutron number $N \sim 88$ should exhibit these correlations. Yet, there remain various nuclei near $Z = 56$ and $N = 88$ for which experimental evidence of octupole correlations has not been recorded. Thus, observation of these correlations can provide useful information about the energy level structure and shape of nuclei with mass number $A\sim144$.


\section*{Purpose}
%Explain what problem they are solving, or what information they were trying to gain.
In this work, experiments are performed to hunt for signs of octupole correlations in $\ce{^{148}Ce}$, which with $Z = 58$ and $N = 90$, should display this type of interaction. The authors also seek to extend the existing picture (\textit{level scheme}) of the excited states of this nuclide.


\section*{Approach}
%Describe explicitly the method they use to complete their work, i.e. the experimental system and measurements, the model design and computational techniques used, or the setup of their equations and the assumptions applied.
A sample of $\ce{^{252}Cf}$ was placed inside a gamma ray detector array, the spontaneous fission of which produced (among other isotopes) $\ce{^{148}Ce}$. Then, gamma rays that were emitted from excited states of the radioisotopes produced by fission events were measured by the detector array. Signals from sources other than $\ce{^{148}Ce}$ were filtered out during the analysis phase.

\medskip
Gamma rays that are recorded with a small enough separation in time (typically $\sim$ns) can be attributed to the decay of an individual nucleus, if enough of these \textit{coincident} detections are made. By using this fact and focussing on gamma rays that are known to be emitted by $\ce{^{148}Ce}$ during their data analysis, a level scheme for $\ce{^{148}Ce}$ was built. Then, the relative intensities of and the measured total internal conversion (where an electron is emitted instead of a gamma ray) coefficients for different gamma ray transitions were used to infer the spin-parities of the observed excited states.

\section*{Contribution}
%Describe their results and conclusions, assess how they fit into the field. Mention any important outcomes or future directions enabled by their work.
20 new transitions and nine new levels were added to the level scheme of $\ce{^{148}Ce}$. Spins and parities were assigned (tentatively in some cases) for some of the newly discovered states and either confirmed or refined for some other existing levels. Internal conversion coefficients for some transitions were also measured, by taking the ratio of the intensity of the electron emission process to the total intensity of transitions from a given excited state. 

\medskip
Nuclei can rotate (or vibrate) in various ways. Within their level schemes, each possible rotation (vibration) is represented by a group of energy levels (\textit{band}) with different energies. Such a band could describe rotation around a given axis at different speeds, for example. By analysing the differences in energies between certain rotational bands of opposite parity, the observed octupole correlations in $\ce{^{148}Ce}$ were suggested to be similar to those found in $\ce{^{144,146}Ce}$. However, it was proposed that the different bands within $\ce{^{148}Ce}$ may exhibit octupole correlations with different strengths. This conclusion was reinforced by further analysis of the relative transition energies and intensities within each rotational band. 

\medskip
Yet, analysis of the moment of inertia as a function of the rotational energy of the nucleus led the authors to suggest that the deformation of this nucleus due to these octupole correlations may be unstable, prompting further theoretical study. 

\section*{Relevance}
%Explain how this paper is relevant to your project and what you are trying to get out of the paper. Does it suggest other papers you should read, or give you new information you need?
While access to ANU's experimental facilities remains heavily restricted due to the COVID-19 pandemic, I will be analysing data from an experiment performed to gauge octupole collectivity in the neutron-rich nuclides $\ce{^{150,152}Ce}$. These are located near $Z=56$ and $N=88$, but remain unstudied. As such, having an understanding of what octupole correlations are and how they can be investigated is vital.

\section*{Quality}
%Discuss the quality of the writing and presentation of results, and try to assess how much you trust their assumptions, approach, and conclusions. You can talk to a supervisor to help you with this.
This work was written clearly and the analysis was detailed, with the development of their final level scheme via gamma ray spectroscopic analysis described in detail. 
However, I did have to refer to some other sources to clarify parts of the paper that I was not familiar with. 

\medskip
These authors also provided multiple pieces of evidence for their conclusion that they did observe octupole correlations in $\ce{^{148}Ce}$, making their conclusions trustworthy. Seeing explicit discussion of how they reached these conclusions was also worthwhile, given I will be performing a similar analysis for my thesis.

\section*{Questions/Directions}
%List any questions the paper has raised, and how you might go about addressing them. Describe any directions your reading/own work could take that are suggested by this paper.
After reading this paper, I should do the following.
\begin{itemize}
\item Brush up on my knowledge of the finer details of nuclear structure, by referring to my notes from PHYS3105 and relevant textbooks.
\item Explore the references of this paper to better understand the theoretical models that predict the existence of these octupole correlations.
\end{itemize}

%\vspace*{-\baselineskip}
%\bibliographystyle{ieeetr}
%\bibliography{references.bib}{}

%Submission details
% So the resubmission assignment is available on Wattle. It is a two-part assignment - submit the feedback file you received in part 2, the actual final journal entry in part 1.	


\end{document}